\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Syed Saheer Multani} \\ \vspace{1pt}
    \small Toronto, ON $|$ \small 647-926-4730 $|$ \href{mailto:saheer.multani@torontomu.ca}{\small{saheer.multani@torontomu.ca}} $|$ 
    \href{https://linkedin.com/in/saheermultani}
    {\underline{linkedin.com/in/saheermultani}} $|$
    \href{https://github.com/blazzzin}
    {\underline{github.com/blazzzin}}
\end{center}

%-----------Summary of Qualifications-----------
\section{Summary of Qualifications}
  \resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{Portfolio Website: \href{https://saheermultani.com}{{\textbf{SAHEERMULTANI.COM}}}}
        \resumeItem{\textbf{4 Months of Paid Software Development Experience:} Gained hands-on experience with API integrations, automation, and data management during an internship, achieving efficiency improvements and scalable solutions.}
        \resumeItem{\textbf{2 Years of Customer Service Experience:} Developed key interpersonal and organizational transferrable skills, including communication, problem-solving, and teamwork, in a client-facing environment.}
        % \resumeItem{Exhibits excellent communication and collaboration skills, effectively working with diverse teams to achieve project goals and mentor peers.}
        % \resumeItem{Strong problem-solving and analytical skills demonstrated through technical roles, including developing comprehensive integrations for Autodesk BIM 360 and optimizing processes to enhance efficiency and scalability.}
        \resumeItem{\textbf{Technical Skills:} Proficient in Java, Python, C/C++, JavaScript, HTML/CSS, VHDL, FPGA, Oscilloscopes, MATLAB, x86 Assembly, XML, LaTeX, Bash, Express.js, JavaFX, Flask, GitHub, MySQL, APIs, Smartsheet.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%   %-----------PROGRAMMING SKILLS-----------
% \section{Summary of Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Languages}{: Java, Python, C/C++, JavaScript, HTML/CSS, VHDL, MATLAB, x86 Assembly, XML, LaTeX, Bash} \\
%      \textbf{Frameworks}{: Express.js, JavaFX, Flask} \\
%      \textbf{Tools}{: Windows, Unix, GitHub, FPGA, VS Code, Visual Studio, Quartus II, Apache Netbeans, CodeWarrior, MySQL, Two-Legged OAuth, SSH, Smartsheet, MS Office, Oscilloscope} \\
%      \textbf{Libraries}{: Tkinter, Python Imaging Library (PIL), Axios, JQuery, Select2}
%     }}
%  \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Engineering: Computer Engineering - Software Engineering Option}{Toronto, ON}
      {Toronto Metropolitan University (Formerly Ryerson University)}{Exp. 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BIM Software Developer Intern}{May 2024 -- August 2024}
      {Loblaw Companies Limited}{Brampton, ON}
      \resumeItemListStart
        \resumeItem{Developed comprehensive integrations for Autodesk BIM 360, creating a Node.js/Express.js solution that added over 425 users to projects, reducing manual onboarding time by 90+\%.}
        \resumeItem{Built an advanced API-based integration to add individual users to over 3,500 projects, cutting down onboarding time by 80+\% and enhancing scalability for future expansions.}
        \resumeItem{Developed Smartsheet-based API applications to automate updates across thousands of entries, drastically reducing manual data entry and enhancing accuracy in project tracking.}
        \resumeItem{Created Smartsheet workflows to archive tasks across 500+ stores, reducing data management time by 70+\% and decreasing administrative workload.}
      \resumeItemListEnd
      \resumeSubheading
      {General Merchandise \& Grocery Clerk}{July 2022 -- July 2024}
      {The Real Canadian Wholesale Club}{Mississauga, ON}
      \resumeItemListStart
        \resumeItem{Provided great customer service by providing to any customers' needs.}
        \resumeItem{Ensured store shelves were organized and that product displays met company standards and were stocked.}
        \resumeItem{\textbf{Skills Gained:} Communication, Customer Service, Team Work \& Collaboration, Time Management, Attention to Detail, Problem-Solving, Responsibility, Product Knowledge, Multitasking, Adaptability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Smart Crafting Display} $|$ \emph{Forge API, Java, Minecraft, and Gradle}}{September 2024 - Present}
          \resumeItemListStart
            \resumeItem{Currently developing a detailed crafting mod/guide in Minecraft to simplify item creation, featuring clear component breakdowns and user-friendly quantity displays.}
            \resumeItem{Designing a visually appealing interface with customizable backgrounds and increased transparency to enhance user experience and accessibility.}
            \resumeItem{Working on a fully operational inventory management system, including features for locking the GUI and resizing options to optimize gameplay.}
        \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{FormatX} $|$ \emph{JavaScript, Python, HTML, CSS, and Flask}}{June - July 2024}
          \resumeItemListStart
            \resumeItem{Created a web application that offers advanced features such as image conversion, PDF merging, and splitting, streamlining document management for users with diverse needs.}
            \resumeItem{Focused on designing an intuitive interface that improves accessibility and engagement, leading to increased user satisfaction and adoption rates.}
            \resumeItem{Developed secure backend processes for efficient file handling, including error-checking mechanisms and optimized processing workflows, ensuring high performance and reliability in document management tasks.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Retail Banking System} $|$ \emph{JavaFX, MySQL, SQL Plus and Bash}}{April - May 2024}
          \resumeItemListStart
            \resumeItem{Developed a retail banking system with a JavaFX GUI and MySQL database, applying object-oriented principles and design patterns for scalability and maintainability.}
            \resumeItem{Created a role-based authentication system, enabling customers to perform transactions (deposits, withdrawals) and employees to manage accounts.}
            \resumeItem{Automated database operations with Bash scripts for table creation, data population, and querying, streamlining data management across branches and headquarters.}
            \resumeItem{Enforced data integrity with unique constraints, credential storage, data reliability, and user experience.}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Central Processing Unit} $|$ \emph{VHDL, FPGA, and Quartus II}}{November - December 2023}
      %     \resumeItemListStart
      %       \resumeItem{Employed Quartus II and VHDL to architect and deploy a custom 8-bit CPU on FPGA, incorporating an Arithmetic and Logic Unit (ALU) and control unit.}
      %       \resumeItem{Engineered a versatile ALU capable of executing multiple arithmetic and logical operations, leveraging a Finite State Machine (FSM) control unit and a 4x16 decoder for opcodes and coordinate operations across components.}
      %       \resumeItem{Simulated and verified design with seven-segment display outputs for result visualization.}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd

%

%-------------------------------------------
\end{document}
